NLIZE: a Perturbation-Driven Visual Interrogation Tool for Analyzing and Interpreting Natural Language Inference Models

### 2018-03-26 paper/paper_entailVis.tex
update background
update teaser
update captions

@@

%% Uncomment below to include a teaser figure.
% \teaser{
%   \centering
%   \includegraphics[width=\linewidth]{CypressView}
%   \caption{In the Clouds: Vancouver from Cypress Mountain. Note that the teaser may not be wider than the abstract block.}
% 	\label{fig:teaser}
% }
\teaser{
% \vspace{-8mm}
 % \includegraphics[width=0.78\linewidth]{teaser}
 \includegraphics[width=.96\linewidth]{teaser.pdf}
 \centering
 % \vspace{-3mm}
  \caption{
 System overview.
  }
\label{fig:teaser}
}

@@

\input{task.tex}
\input{pipeline.tex}
\input{perturbation.tex} % how to do the perturbation
\input{sentence.tex}
\input{attention.tex} % how to encode the information
\input{prediction.tex}

>>>>

\usepackage{tikz}
\def\checkmark{\tikz\fill[scale=0.4](0,.35) -- (.25,0) -- (1,.7) -- (.25,.15) -- cycle;}

@@

%% Uncomment below to include a teaser figure.
% \teaser{
%   \centering
%   \includegraphics[width=\linewidth]{CypressView}
%   \caption{In the Clouds: Vancouver from Cypress Mountain. Note that the teaser may not be wider than the abstract block.}
% 	\label{fig:teaser}
% }
\teaser{
% \vspace{-8mm}
 % \includegraphics[width=0.78\linewidth]{teaser}
 \includegraphics[width=1.0\linewidth]{teaser.pdf}
 \centering
 % \vspace{-3mm}
  \caption{
The interface of the NLIZE system. During exploration, we can filter through large number of sentence examples summarized in (A) and select the example of interests displayed in (B). The model internal information (attention) is displayed (D) and (E). The predicted probability (one of three labels: \emph{neural}, \emph{entailment}, \emph{contradiction}) is shown in the barycentric coordinate in (F). Finally, the high-level model structure and the updates to the model are summarized in (C).
}
\label{fig:teaser}
}

@@

\input{task.tex}
\input{overview.tex}

\input{sentence.tex}
\input{attention.tex} % how to encode the information
\input{prediction.tex}
\input{pipeline.tex}
\input{predSummary.tex}

### 2018-03-26 paper/predSummary.tex
update teaser

%treemap for prediction
We utilized a treemap (a) to encode the ground truth label and the model prediction generated by the
By click on the treemap cell, we can narrow down the selection by focus on specific senarios.

\begin{figure}[htbp]
\centering
\vspace{-2mm}
 \includegraphics[width=1.0\linewidth]{summaryView}
 \caption{
Summarize the prediction results and sensitivity of the entire development set, and provide an explorative interface to select example of interests.
We summarize all the prediction results in (a), where the green block indicates correct predictions, and orange block indicates wrong predictions, and the label (e.g., E/E, E/N) indicates the ground truth label and the predicted label (N-Neural, E-Entailment, C-Contradiction).
%
The user can select the treemap to focus on the specific type of senarios and reveal the histogram (b) and scatterplot (c) for displaying per-pair information on the selected subset.
The selection can be further narrowed down by select the bin in the histogram.
In (c) and (d), each point corresponds to one prediction.
 }
\label{fig:modelPipeline}
\end{figure}

>>>>

%treemap for prediction
As illustrate in Fig.~\ref{fig:summaryView}, we utilized a treemap (a) to encode the ground truth label and the model prediction generated by the
By click on the treemap cell, we can narrow down the selection by focus on specific senarios.

\begin{figure}[htbp]
\centering
\vspace{-2mm}
 \includegraphics[width=1.0\linewidth]{summaryView}
 \caption{
Summarize the prediction results and sensitivity of the entire development set, and provide an explorative interface to select example of interests.
We summarize all the prediction results in (a), where the green block indicates correct predictions, and orange block indicates wrong predictions, and the label (e.g., E/E, E/N) indicates the ground truth label and the predicted label (N-Neural, E-Entailment, C-Contradiction).
%
The user can select the treemap to focus on the specific type of senarios and reveal the histogram (b) and scatterplot (c) for displaying per-pair information on the selected subset.
The selection can be further narrowed down by select the bin in the histogram.
In (c) and (d), each point corresponds to one prediction.
 }
\label{fig:summaryView}
\end{figure}
